Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-09 WSSSPE3/report/wg_appendix_funding_spec_expert.tex
Fix typos

``Are you an RSE or a RA?'' -- this is not properly a binary question. Most of
us sit at different points on that spectrum, and move along it during our
careers. (Ususally from RA to RSE -- examples of movement in the other direction
from readers would be welcomed.)
Either way, the label ``Research Software Engineer'' is now starting to
have some power. Many scientists do not want to be writing code; some do, to
varying degrees. These groups can usefully support each other.

@@

Collaborative funding can be important for RSE groups, to ensure that research
leadership remains with the domain scientists. At NCAR, University partnerships
are required for submission of proposals, so collaboration is an essential part
of grant submission, and this will tend to bring developers and
scientists together. The UCL group also follows this approach, with all bids
requiring an academic collaborator.
Domain scientists and developers are funded together in a single proposal.
Another example of a success is the development of semantics and linked data in
support of Ocean Sciences. An Earthcube funded project pairs domain scientists
with RSEs and has been successful as the semantics attached have increased data
use and discovery significantly.

@@

We think support from non-governmental organizations will be important if RSE
groups will become established.
The Sloan Foundation is currently funding data science engineers, who work in
the context of other SW developers at University of Washington.
These scientists work in the e-Science Studio/dataScience Studio, and they
help a group of graduate students in solving their problems in data
science and data management. During Fall and Spring, a 10-week incubator program
allows students to work two days a week to work on a data-intensive science
project. Some fraction of the developer time is dedicated to the developers'
personal interests as well as instruction.

>>>>

``Are you an RSE or a RA?'' -- this is not properly a binary question. Most of
us sit at different points on that spectrum, and move along it during our
careers. (Usually from RA to RSE -- examples of movement in the other direction
from readers would be welcomed.)
Either way, the label ``Research Software Engineer'' is now starting to
have some power. Many scientists do not want to be writing code; some do, to
varying degrees. These groups can usefully support each other.

@@

Collaborative funding can be important for RSE groups, to ensure that research
leadership remains with the domain scientists. At NCAR, University partnerships
are required for submission of proposals, so collaboration is an essential part
of grant submission, and this will tend to bring developers and
scientists together. The UCL group also follows this approach, with all bids
requiring an academic collaborator.
Domain scientists and developers are funded together in a single proposal.
Another example of a success is the development of semantics and linked data in
support of Ocean Sciences. An EarthCube funded project pairs domain scientists
with RSEs and has been successful as the semantics attached have increased data
use and discovery significantly.

@@

We think support from non-governmental organizations will be important if RSE
groups will become established.
The Sloan Foundation is currently funding data science engineers, who work in
the context of other SW developers at University of Washington.
These scientists work in the e-Science Studio/Data Science Studio, and they
help a group of graduate students in solving their problems in data
science and data management. During Fall and Spring, a 10-week incubator program
allows students to work two days a week to work on a data-intensive science
project. Some fraction of the developer time is dedicated to the developers'
personal interests as well as instruction.
